---
title: "Lab 01 - Hello R"
author: "Rebecca Smith"
date: "02/02/2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

This file has 1846 rows and 3 columns. The variables incldued in the data frame are the dataset, the x-values, and the y-values.

### Exercise 2

Below is a visualization of the dino dataset.

```{r plot-dino, fig.height=5, fig.width=7}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between the x and y values in the dino dataset is -0.06.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Below is the visualization for the star dataset.

```{r plot-star, fig.height=5, fig.width=7}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y))+
  geom_point()

```

The correlation for the star data, r = -0.06, is the same as the correlation found for the dino data.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Below is a visualization of the circle data.The correlation between x and y for the circle data is approximately -0.07. Thus, the correlation between x and y in this dataset is slightly more negative than the star or the dino datasets.

```{r plot-circle, fig.height=5, fig.width=7}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes (x = x, y = y))+
  geom_point()

```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))

```

### Exercise 5

Below is a visualization of all three datasets and their correlations.

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3)+
  theme(legend.position = "none")
```

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
